Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-07-07 manuscript/supporting_information.Rmd
updates subscripting and model statements re MBH edits

**Full expression of posterior and joint distributions**
\begin{align}
[\boldsymbol{\beta_0}, \tilde{\beta_0}, \boldsymbol{\beta_s}, \tilde{\beta_s}, \boldsymbol{\beta_Q}, \boldsymbol{\beta_c}, \beta_{d,1}, \beta_{d,2}, \sigma_Q^2, \sigma_{\beta_0}^2, \sigma_{\beta_s}^2 | y_{i,q,t}^{S}] &\propto \\
&\prod_{t=1}^T \prod_{i=1}^n [y_{i,q,t}^{S} | \beta_{0,t}, \beta_{s,t}, \beta_{Q}, \boldsymbol{\beta_c}, \beta_{d,1}, \beta_{d,2}] \times \\
&[\beta_{0,t} | \tilde{\beta_0}, \sigma_{\beta_0}^2] \times \\
&[\beta_{s,t} | \tilde{\beta_s}, \sigma_{\beta_s}^2] [\boldsymbol{\beta_c}|\sigma_{\beta_c}^2 \textbf{I}] \times \\
&\prod_{q=1}^{Q_{tot}} [\beta_{Q,q} | \sigma_Q^2] \times \\
&[\beta_{d,1}] [\beta_{d,1}] [\tilde{\beta_0}] [\tilde{\beta_s}] [\sigma_Q] [\sigma_{\beta_0}] [\sigma_{\beta_s}]
\end{align}

@@

**Data, process, and parameter models.**
\begin{align}
&\mathtt{data} \qquad &y_{i,q,t+1}^G \sim \text{Normal}(\mu_{i,q,t+1}, \sigma^2_{x_{i,q,t+1}}) \\
&\mathtt{process} \qquad &\mu_{i,q,t+1} = \beta_{0,t} + \beta_{s,t}x_{i,q,t} + \beta_{Q,q} + \textbf{z}'_t \boldsymbol{\beta}_c + \beta_{d,1} w_{i,q,t} + \beta_{d,2} (x_{i,q,t}w_{i,q,t}) \\
& \qquad & \sigma^2_{iQ,t} = ae^{b\mu_{iQ,t+1}} \\
&\mathtt{parameters} \qquad &\beta_{0,t} \sim \text{Normal}(\tilde{\beta_0}, \sigma_{\beta_0}^2)\\
& \qquad & \beta_{s,t} \sim \text{Normal}(\tilde{\beta_s}, \sigma_{\beta_s}^2) \\
& \qquad & \boldsymbol{\beta_{Q,q}} \sim \text{Normal}(0, \sigma_Q^2) \\
& \qquad & \boldsymbol{\beta}_c \sim \text{Normal}(\textbf{0}, \sigma_c^2 \textbf{I}) \\
& \qquad & \beta_{d,1} \sim \text{Normal}(0, 100) \\
& \qquad & \beta_{d,2} \sim \text{Normal}(0, 100) \\
& \qquad & \tilde{\beta_0} \sim \text{Normal}(0, 100) \\
& \qquad & \tilde{\beta_s} \sim \text{Normal}(0, 100) \\
& \qquad & \sigma_Q \sim \text{Cauchy}(0, 5) \\
& \qquad & \sigma_{\beta_0} \sim \text{Cauchy}(0, 5) \\
& \qquad & \sigma_{\beta_s} \sim \text{Cauchy}(0, 5) \\
& \qquad & a \sim \text{Normal}(0, 100) \\
& \qquad & b \sim \text{Normal}(0, 100)
\end{align}

**Full expression of posterior and joint distributions**
\begin{align}
[\boldsymbol{\beta_0}, \tilde{\beta_0}, \boldsymbol{\beta_s}, \tilde{\beta_s}, \boldsymbol{\beta_Q}, \boldsymbol{\beta_c}, \beta_{d,1}, \beta_{d,2}, \sigma_Q^2, \sigma_{\beta_0}^2, \sigma_{\beta_s}^2,a,b | y_{i,q,t+1}^G] &\propto \\
&\prod_{t=1}^T \prod_{i=1}^n [y_{i,q,t+1}^G | \beta_{0,t}, \beta_{s,t}, \beta_{Q}, \boldsymbol{\beta_c}, \beta_{d,1}, \beta_{d,2}, a, b] \times \\
&[\beta_{0,t} | \tilde{\beta_0}, \sigma_{\beta_0}^2] \times \\
&[\beta_{s,t} | \tilde{\beta_s}, \sigma_{\beta_s}^2] [\boldsymbol{\beta_c}|\sigma_{\beta_c}^2 \textbf{I}] \times \\
&\prod_{q=1}^{Q_{tot}} [\beta_{Q,q} | \sigma_Q^2] \times \\
&[\beta_{d,1}] [\beta_{d,1}] [\tilde{\beta_0}] [\tilde{\beta_s}] [\sigma_Q] [\sigma_{\beta_0}] [\sigma_{\beta_s}] [a] [b]
\end{align}

@@

**Full expression of posterior and joint distributions**
\begin{align}
[\boldsymbol{\beta_0}, \tilde{\beta}, \boldsymbol{\beta_Q}, \boldsymbol{\beta_c}, \beta_{d}, \sigma_Q^2, \sigma_{\beta_0}^2, \phi, u | y^{R}_{q,t+1}] &\propto \\
&\prod_{t=1}^T \prod_{i=1}^n [y^{R}_{q,t+1} | \beta_{0,t}, \beta_{Q}, \beta_d, \boldsymbol{\beta_c}, \phi, u] \times \\
&[\beta_{0,t} | \tilde{\beta}, \sigma_{\beta_0}^2] [\boldsymbol{\beta_c}|\sigma_{\beta_c}^2 \textbf{I}] \times \\
&\prod_{q=1}^{Q_{tot}} [\beta_{Q,q} | \sigma_Q^2] [\boldsymbol{\beta_c}] [\beta_d] [\tilde{\beta_0}] [\sigma_Q] [\sigma_{\beta_0}] [\phi] [u]
\end{align}

@@

**Full expression of posterior and joint distributions**
\begin{align}
[\boldsymbol{\beta_0}, \tilde{\beta_0}, \boldsymbol{\beta_s}, \tilde{\beta_s}, \boldsymbol{\beta_Q}, \boldsymbol{\beta_c}, \sigma_Q^2, \sigma_{\beta_0}^2, \sigma_{\beta_s}^2, \sigma^2 | y_{q,t+1}^{P}] &\propto \\
&\prod_{t=1}^T \prod_{i=1}^n [y_{q,t+1} | \beta_{0,t}, \beta_{s,t}, \beta_{Q,q}, \boldsymbol{\beta_c}] \times \\
&[\beta_{0,t} | \tilde{\beta_0}, \sigma_{\beta_0}^2] \times \\
&[\beta_{s,t} | \tilde{\beta_s}, \sigma_{\beta_s}^2] [\boldsymbol{\beta_c}|\sigma_{\beta_c}^2 \textbf{I}] \times \\
&\prod_{q=1}^{Q_{tot}} [\beta_{Q,q} | \sigma_Q^2] \times \\
&[\tilde{\beta_0}] [\tilde{\beta_s}] [\sigma_Q] [\sigma_{\beta_0}] [\sigma_{\beta_s}] [\sigma]
\end{align}

>>>>

**Full expression of posterior and joint distributions**
\begin{align}
[\boldsymbol{\beta_0}, \tilde{\beta_0}, \boldsymbol{\beta_s}, \tilde{\beta_s}, \boldsymbol{\beta_Q,q}, \boldsymbol{\beta_c}, \beta_{d,1}, \beta_{d,2}, \sigma_Q^2, \sigma_{\beta_0}^2, \sigma_{\beta_s}^2 | y_{i,q,t}^{S}] &\propto \\
&\prod_{t=1}^T \prod_{i=1}^n [y_{i,q,t}^{S} | \beta_{0,t}, \beta_{s,t}, \beta_{Q}, \boldsymbol{\beta_c}, \beta_{d,1}, \beta_{d,2}] \times \\
&[\beta_{0,t} | \tilde{\beta_0}, \sigma_{\beta_0}^2] \times \\
&[\beta_{s,t} | \tilde{\beta_s}, \sigma_{\beta_s}^2] [\boldsymbol{\beta_c}|\sigma_{\beta_c}^2] \times \\
&\prod_{q=1}^{Q_{tot}} [\beta_{Q,q} | \sigma_Q^2] \times \\
&[\beta_{d,1}] [\beta_{d,1}] [\tilde{\beta_0}] [\tilde{\beta_s}] [\sigma_Q] [\sigma_{\beta_0}] [\sigma_{\beta_s}]
\end{align}

@@

**Data, process, and parameter models.**
\begin{align}
&\mathtt{data} \qquad &y_{i,q,t+1}^G \sim \text{Normal}(\mu_{i,q,t+1}, \sigma^2_{x_{i,q,t+1}}) \\
&\mathtt{process} \qquad &\mu_{i,q,t+1} = \beta_{0,t} + \beta_{s,t}x_{i,q,t} + \beta_{Q,q} + \textbf{z}'_t \boldsymbol{\beta}_c + \beta_{d,1} w_{i,q,t} + \beta_{d,2} (x_{i,q,t}w_{i,q,t}) \\
& \qquad & \sigma^2_{iQ,t} = ae^{b\mu_{iQ,t+1}} \\
&\mathtt{parameters} \qquad &\beta_{0,t} \sim \text{Normal}(\tilde{\beta_0}, \sigma_{\beta_0}^2)\\
& \qquad & \beta_{s,t} \sim \text{Normal}(\tilde{\beta_s}, \sigma_{\beta_s}^2) \\
& \qquad & \beta_{Q,q} \sim \text{Normal}(0, \sigma_Q^2) \\
& \qquad & \boldsymbol{\beta}_c \sim \text{Normal}(\textbf{0}, \sigma_c^2 \textbf{I}) \\
& \qquad & \beta_{d,1} \sim \text{Normal}(0, 100) \\
& \qquad & \beta_{d,2} \sim \text{Normal}(0, 100) \\
& \qquad & \tilde{\beta_0} \sim \text{Normal}(0, 100) \\
& \qquad & \tilde{\beta_s} \sim \text{Normal}(0, 100) \\
& \qquad & \sigma_Q \sim \text{Cauchy}(0, 5) \\
& \qquad & \sigma_{\beta_0} \sim \text{Cauchy}(0, 5) \\
& \qquad & \sigma_{\beta_s} \sim \text{Cauchy}(0, 5) \\
& \qquad & a \sim \text{Normal}(0, 100) \\
& \qquad & b \sim \text{Normal}(0, 100)
\end{align}

**Full expression of posterior and joint distributions**
\begin{align}
[\boldsymbol{\beta_0}, \tilde{\beta_0}, \boldsymbol{\beta_s}, \tilde{\beta_s}, \beta_{Q,q}, \boldsymbol{\beta_c}, \beta_{d,1}, \beta_{d,2}, \sigma_Q^2, \sigma_{\beta_0}^2, \sigma_{\beta_s}^2,a,b | y_{i,q,t+1}^G] &\propto \\
&\prod_{t=1}^T \prod_{i=1}^n [y_{i,q,t+1}^G | \beta_{0,t}, \beta_{s,t}, \beta_{Q}, \boldsymbol{\beta_c}, \beta_{d,1}, \beta_{d,2}, a, b] \times \\
&[\beta_{0,t} | \tilde{\beta_0}, \sigma_{\beta_0}^2] \times \\
&[\beta_{s,t} | \tilde{\beta_s}, \sigma_{\beta_s}^2] [\boldsymbol{\beta_c}|\sigma_{\beta_c}^2] \times \\
&\prod_{q=1}^{Q_{tot}} [\beta_{Q,q} | \sigma_Q^2] \times \\
&[\beta_{d,1}] [\beta_{d,1}] [\tilde{\beta_0}] [\tilde{\beta_s}] [\sigma_Q] [\sigma_{\beta_0}] [\sigma_{\beta_s}] [a] [b]
\end{align}

@@

**Full expression of posterior and joint distributions**
\begin{align}
[\boldsymbol{\beta_0}, \tilde{\beta}, \boldsymbol{\beta_Q}, \boldsymbol{\beta_c}, \beta_{d}, \sigma_Q^2, \sigma_{\beta_0}^2, \phi, u | y^{R}_{q,t+1}] &\propto \\
&\prod_{t=1}^T \prod_{i=1}^n [y^{R}_{q,t+1} | \beta_{0,t}, \beta_{Q,q}, \beta_d, \boldsymbol{\beta_c}, \phi, u] \times \\
&[\beta_{0,t} | \tilde{\beta}, \sigma_{\beta_0}^2] [\boldsymbol{\beta_c}|\sigma_{\beta_c}^2] \times \\
&\prod_{q=1}^{Q_{tot}} [\beta_{Q,q} | \sigma_Q^2] [\boldsymbol{\beta_c}] [\beta_d] [\tilde{\beta_0}] [\sigma_Q] [\sigma_{\beta_0}] [\phi] [u]
\end{align}

@@

**Full expression of posterior and joint distributions**
\begin{align}
[\boldsymbol{\beta_0}, \tilde{\beta_0}, \boldsymbol{\beta_s}, \tilde{\beta_s}, \boldsymbol{\beta_Q}, \boldsymbol{\beta_c}, \sigma_Q^2, \sigma_{\beta_0}^2, \sigma_{\beta_s}^2, \sigma^2 | y_{q,t+1}^{P}] &\propto \\
&\prod_{t=1}^T \prod_{i=1}^n [y_{q,t+1} | \beta_{0,t}, \beta_{s,t}, \beta_{Q,q}, \boldsymbol{\beta_c}] \times \\
&[\beta_{0,t} | \tilde{\beta_0}, \sigma_{\beta_0}^2] \times \\
&[\beta_{s,t} | \tilde{\beta_s}, \sigma_{\beta_s}^2] [\boldsymbol{\beta_c}|\sigma_{\beta_c}^2] \times \\
&\prod_{q=1}^{Q_{tot}} [\beta_{Q,q} | \sigma_Q^2] \times \\
&[\tilde{\beta_0}] [\tilde{\beta_s}] [\sigma_Q] [\sigma_{\beta_0}] [\sigma_{\beta_s}] [\sigma]
\end{align}
